\bf\mftitle

### 2011-02-21 doc/jInfer/treeruledisplayer/treeruledisplayer.tex
Added Documentation for Tree rule displayer
#3187360 improved TreeRD documentation.

\def\mftitle{jInfer BasicRuleDisplayer Module Description}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

This rule displayer uses JUNG graph implementation to draw rules as forest of trees, where each tree represents one rule of whole set. In each tree, root vertex represents left side of the rule, inner vertices represents concatenation, alternation or permutation and leafs are elements, attributes or simple data. As in basic rule displayer it creates a component with multiple tabs: each one for a new grammar to display.

@@

Main window of rule displayer may have multiple tabs in it: each contains its own \code{RuleDisplayer} responsible for rendering specified grammar using \jmodule{JUNG} library.\\

All the trees representing rules are created in the \code{GraphBuilder} class with method \code{buildGraphPanel()}. While the code itself is a nice recursion programming exercise, there is nothing of a special interest in it.\\

>>>>

\def\mftitle{jInfer TreeRuleDisplayer Module Description}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

This rule displayer uses JUNG graph implementation to draw rules as forest of trees, where each tree represents one rule of whole set. In each tree, root vertex represents left side of the rule, inner vertices represents concatenation, alternation or permutation and leafs are elements, simple data or attribute. As in basic rule displayer it creates a component with multiple tabs: each one for a new grammar to display.

@@

Main window of rule displayer may have multiple tabs in it: each contains its own \code{RuleDisplayer} responsible for rendering specified grammar using \jmodule{JUNG} library. Each tab in rule displayer window is represented by instance of \code{RulePanel} which contains button linking to options and the main panel(canvas) with rendered rules. Canvas is made by \code{VisualizationViewer} instance with \code{TreeLayout} layout which are both classes from JUNG library. For \code{VisualizationViewer} is set \code{GraphMouse} with transforming mode allowing zooming and moving of graph in canvas. To allow user set custom appearance of rules, we set various \code{Transformer}s in \code{RenderContext} of \code{VisualizationViewer}. These transormers change color, shape and size vertices in each rule tree according to properties set in options.\\

All the trees representing rules are created in the \code{GraphBuilder} class with method \code{buildGraphPanel()}. This method creates \code{DelegateForrest} of \code{DelegateTree}s where each tree of the forrest represents one rule. Each vertex of the tree is represented by \code{Regexp<? extends AbstractNamedNode>} and edge by \code{RegexpInterval}. While the code building tree structure is a nice recursion programming exercise, there is nothing of a special interest in it. Finally the method appends forrest into layout and visualizationViewer which were described above. All code responsible for building rule trees is contained in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.logic}. For more details about JUNG library please see \cite{jung}.\\
